Plug-and-play dual-tree algorithm runtime analysis

### 2015-08-14 bounds-files/sec01-supporting-lemmas.tex
Bibliography changes, I want to stab myself, I hate this shit so much.
Add an example cover tree figure.

Note that the cover tree may be interpreted as an infinite-leveled tree, with
$C_{\infty}$ containing only the root point, $C_{-\infty} = S$, and all levels
between defined as above.  \citet{langford2006} find
this representation (which they call the {\it implicit} representation) easier
for description of their algorithms and some of their proofs.  But clearly,
this is not suitable for implementation; hence, there is an {\it explicit}
representation in which all nodes that have only a self-child are coalesced
upwards (that is, the node's self-child is removed, and the children of that
self-child are taken to be the children of the node).  Figure
\ref{fig:implicit-explicit} shows an example cover tree and highlights implicit
and explicit nodes.

@@

>>>>

Note that the cover tree may be interpreted as an infinite-leveled tree, with
$C_{\infty}$ containing only the root point, $C_{-\infty} = S$, and all levels
between defined as above.  \citet{langford2006} find
this representation (which they call the {\it implicit} representation) easier
for description of their algorithms and some of their proofs.  But clearly,
this is not suitable for implementation; hence, there is an {\it explicit}
representation in which all nodes that have only a self-child are coalesced
upwards (that is, the node's self-child is removed, and the children of that
self-child are taken to be the children of the node).  Figure
\ref{fig:example-cover-tree} shows each of the levels of an example cover tree
(in the explicit representation) on a simple six-point dataset.

@@

\begin{figure}
\begin{subfigure}[b]{0.495\textwidth}
  \begin{center}
    \begin{tikzpicture}[scale=0.8]
      \input{figures/cover-tree-points}
      \input{figures/cover-tree-s1}
    \end{tikzpicture}
  \end{center}
  \vspace*{-0.5em}
  \caption{Root node at scale $1$.}
  \label{fig:cover-tree-s1}
\end{subfigure}
\begin{subfigure}[b]{0.495\textwidth}
  \begin{center}
    \begin{tikzpicture}[scale=0.85]
      \input{figures/cover-tree-points}
      \input{figures/cover-tree-s0}
    \end{tikzpicture}
  \end{center}
  \vspace*{-0.5em}
  \caption{Nodes at scale $0$.}
  \label{fig:cover-tree-s0}
\end{subfigure}
\begin{subfigure}[b]{0.355\textwidth}
  \begin{center}
    \begin{tikzpicture}[scale=0.85]
      \input{figures/cover-tree-points}
      \input{figures/cover-tree-s-1}
    \end{tikzpicture}
  \end{center}
  \vspace*{-0.5em}
  \caption{Nodes at scale $-1$.}
  \label{fig:cover-tree-s-1}
\end{subfigure}
\begin{subfigure}[b]{0.64\textwidth}
  \begin{center}
    \begin{tikzpicture}[scale=0.6]
      \input{figures/cover-tree-ex}
    \end{tikzpicture}
  \end{center}
  \vspace*{-0.5em}
  \caption{Abstract representation.}
  \label{fig:cover-tree-ex}
\end{subfigure}
  \vspace*{-0.5em}
\caption{Example cover tree on six points.  (a) $\mathscr{N}_a$ is centered at
$p_0$ with scale $1$.  (b) $\mathscr{N}_b$ and $\mathscr{N}_c$ are centered at
$p_0$ and $p_1$, respectively, and have scale $0$.  (c) $\mathscr{N}_d$ and
$\mathscr{N}_e$ are centered at $p_0$ and $p_2$, respectively, and have scale
$-1$.  The leaves, $\mathscr{N}_0$ through $\mathscr{N}_6$, are centered at each
of the six points, with scale $-\infty$ (and therefore radius 0).  Note that
although node $\mathscr{N}_b$ in subfigure (b) overlaps node $\mathscr{N}_c$,
point $p_1$ only belongs to $\mathscr{N}_c$, not $\mathscr{N}_b$.  Note also
that this is only one valid cover tree that could be built on the data; other
configurations are possible; for instance, selecting a different root point
gives different valid cover trees.}
\label{fig:example-cover-tree}
\end{figure}
